%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cies Resume/CV
% LaTeX Template
% Version 1.1 (20/7/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Cies Breijs (cies@kde.nl)
% https://github.com/cies/resume with extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[12pt,a4paper]{article} % Font size (10-12pt) and paper size (a4paper, letterpaper, legalpaper, etc)
\usepackage[utf8]{inputenc}
\usepackage[none]{hyphenat}
\include{structure} % Include structure.tex which contains packages and document layout definitions

\hyphenation{Some-long-word} % Specify custom hyphenation points in words with dashes where you would like hyphenation to occur, or alternatively, don't put any dashes in a word to stop hyphenation altogether

\begin{document} 

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

%\maintitle{Benjamin Sarti}{May 23\textsuperscript{rd}, 1990}  % Your name and date of birth or subtitle

\maintitle{Benjamin Sarti}{} 
\\
\begin{small}
\noindent\href{mailto:benjamin.sarti@gmail.com}{benjamin.sarti@gmail.com} \bull Skype: benjaminsarti \bull % Your email address
\textsmaller{+}91 98181-87458 \bull Nationality: French\\ % Your URL
Address: 88 Kailash Hills (2d floor), East of Kailash - 110065 New Delhi, India % Your address
\end{small}


\spacedhrule{0.9em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	objective SECTION
%----------------------------------------------------------------------------------------

\roottitle{Objective} % Root section title

%\vspace{-1.3em} % Reduce whitespace after the Summary heading and the two-column content

French Electrical and General Engineer \textbf{holding a Working Holiday Visa for New Zealand} and looking for a full-time job in software development, telecommunications, automation, systems or test engineering.
%\begin{multicols}{2}  % Start a two-column layout
%\noindent \textit{A summary of your interests, achievements, history, topic of study or any other short summary of your professional life.}\\\\
%Lorem ipsum dolor sit amet, consectetur adipiscing elit. Nunc iaculis scelerisque vestibulum. Sed ut sapien et dui mollis condimentum. Phasellus enim lectus, dignissim vitae velit sit amet, porttitor tincidunt lectus. Vivamus adipiscing volutpat lacinia. Sed dui ipsum, iaculis id facilisis sed, dapibus quis lacus. Quisque blandit hendrerit malesuada. Nunc sollicitudin nisl nunc, vitae luctus leo tincidunt vel.

%Pellentesque bibendum convallis adipiscing. Suspendisse facilisis id massa a lacinia. Nullam odio nibh, placerat at fermentum in, tincidunt eu ipsum. Nullam adipiscing lacus id dui suscipit commodo. Vestibulum iaculis leo imperdiet, porta lorem eu, tempus tortor. Donec interdum risus ullamcorper, vestibulum nulla ut, tincidunt ante. Duis adipiscing auctor nisi, quis tempor tortor ornare aliquet. Aenean at tempor leo. Nam eleifend venenatis elit id aliquet. Mauris quis lacinia dolor, a posuere tellus. Suspendisse nec augue pretium, condimentum risus vitae, dignissim tellus. Proin gravida ante eget massa lacinia consequat. Integer pharetra vel ligula sed vulputate. Integer eget erat quam. Proin adipiscing lorem ac purus adipiscing, non ullamcorper nisi porttitor. 
%\end{multicols}

\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\roottitle{Experience} % Top level section

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.famoco.com/}{Famoco}}
{\textsc{New Delhi, India}} {

\headedsubsection % Job title entry for the current employer
{IT Support Engineer}
{Jun. 2016 -- Present}
{\bodytext{\bull Helping our clients to integrate their Android applications on \href{https://en.wikipedia.org/wiki/Near_field_communication}{NFC} readers; \\
\bull Developed Android applications to interact with Famoco devices (NFC, connectivity, notifications, ...) for technical support and presales.\\
}}
}

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{https://www.cpqd.com.br/en/}{CPQD}}
{\textsc{Campinas, Brazil}} {

\headedsubsection % Job title entry for the current employer
{R\&D Engineer}
{Aug. 2014 -- May 2016}
{\bodytext{\bull \textbf{\emph{Optical amplifiers:}} simulations with MATLAB and OptiSystem to optimize EDF and Raman amplifiers performance. Laboratory automation with LabVIEW and Matlab for optical characterizations. Interacted with several processors and measuring instruments using serial, GPIB, ethernet and USB communications. Integration tests (hardware + firmware) using command-line user interfaces. \\
\bull \textbf{\emph{Integrated Tunable Laser Assembly:}} built a laboratory setup for automated optical characterization using Python and C. Controlled the integrated lasers through serial port and writing hexadecimal commands in the processor registers. Controlled the measuring instrument (Optical/Electrical Spectrum Analyzers, polarization meters) using PyVISA. \\
\bull \textbf{\emph{Packaging for integrated photonics:}} automated DC motors and piezoelectric transducers using Python for free space alignment of polarization multiplexers. The control was done sending hexadecimal commands to the controllers registers through serial port.
}}

\headedsubsection % Job title entry for the current employer
{Intern}
{Jul. 2013 -- Aug. 2014}
{\bodytext{\textbf{\emph{Optical networks:}} implemented \href{http://dx.doi.org/10.1364/OFC.2015.Tu3H.5}{dynamic channels equalization algorithms in C++} on CPqD's testbed and controlled a cascade of optical nodes independently using multithreading. The nodes were controlled using Software Defined Networking and NETCONF protocol. Each node, forming a PII control loop, was constituted of three embedded subsystems (an optical amplifier, an Optical Channel Monitor and a Wavelength Selective Switch) that were controlled by BeagleBords or their own hardware.  }}
}
%------------------------------------------------

%\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
%{\href{http://www.fresnel.fr/spip/}{Institut Fresnel}}
%{\textsc{Marseille, France}} {

%\headedsubsection % Job title entry for the current employer
%{Intern}
%{Jun. 2012 -- Jul. 2012}
%{\bodytext{Optimized the optical filtering of plasmonic structures using MATLAB.}}
%}


%------------------------------------------------

\spacedhrule{-0.2em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\roottitle{Education} % Top level section

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.fee.unicamp.br/node/25}{Universidade Estadual de Campinas}}
{\textsc{Campinas, Brazil}} {

\headedsubsection % Job title entry for the current employer
{Master of Electrical Engineering}
{Jul. 2014 -- Dec. 2015}
{\bodytext{
Nonlinear programming, Information theory, Optical links and Probability theory. \\
\emph{Dissertation title:} \href{http://www.bibliotecadigital.unicamp.br/document/?code=000963393}{"Field Calibration Procedure for Enhanced Automatic Gain Control of Distributed Counter-Propagating Raman Amplifiers."}
}}
}

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{https://www.centrale-marseille.fr/}{École Centrale Marseille}}
{\textsc{Marseille, France}} {

\headedsubsection % Job title entry for the current employer
{Engineer's Degree (French \textit{Diplôme d'Ingénieur})}
{Sept. 2010 -- Nov. 2014}
{\bodytext{Multidisciplinary formation in sciences (Mathematics, Physics); in engineering (Solid and Fluid Mechanics, Heat transfer,  Chemistry, Electronics, ...) and in social sciences (Management, Economics, foreign languages,...).}}
}

%------------------------------------------------

%\begin{Large}
%\textbf{Benjamin Sarti}
%\end{Large}

%\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after
%\vspace{0.7em}

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.fee.unicamp.br/cg}{Universidade Estadual de Campinas}}
{\textsc{Campinas, Brazil}} {

\headedsubsection % Job title entry for the current employer
{Bachelor of Electrical Engineering}
{Jul. 2012 -- Jul. 2014} 

{\bodytext{{\bodytext{Telecommunications, Electronics, Control Engineering and Power Engineering.

\textbf{Embedded systems projects}: \bull Programmed micro-controllers with Process Expert and Code Warrior. Controlled physical systems using GPIO pins and interruptions. 

\bull Built an digital-to-analog converter using a  R–2R ladder and a Raspberry Pi. }}}}
}

\spacedhrule{-0.2em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%------------------------------------------------

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\roottitle{Skills} % Top level section

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Programming Languages:}
{Python, MATLAB, LabVIEW, Java, XML, C and C++.}

\inlineheadsection
{Operating Systems:} 
{Linux, Windows and Android.}

\inlineheadsection
{Others:} 
{OptiSystem, \LaTeX, Git, Jira, TestLink, Zoho, MySQL, Confluence, EAGLE, Inventor.}

%------------------------------------------------
\vspace{0.18cm}
\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Natural languages:}
{Fluent in English, French and Portuguese. Intermediate in Spanish.}

%------------------------------------------------

\spacedhrule{1.6em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	PUBLICATIONS AND PATENT
%----------------------------------------------------------------------------------------

\roottitle{Publications} % Top level section

{\bodytext{\bull J. Januario, M. G. Alabarce, \textbf{B. Sarti}, N. G. Gonzalez, and J. R. F. Oliveira, {\href{http://dx.doi.org/10.1364/OFC.2015.Tu3H.5}{"Experimental demonstration of overshoot suppression for cascaded WSS-based ROADMs,"}} in \textit{Optical Fiber Communication Conference}, Los Angeles, Optical Society of America, pp. Tu3H-5., 2015.}
}
{\bodytext{\bull \textbf{B. Sarti}, M. G. Alabarce, Benoît C. M. Roulle, Israel J. G. Cassimiro, Uiara C. Moura, J. R. F. Oliveira and Max H. M. Costa, {\href{http://ieeexplore.ieee.org/xpl/login.jsp?tp=&arnumber=7369053&url}{"Field calibration procedure for enhanced automatic gain control of distributed Raman amplifiers,"}} in \textit{2015 SBMO/IEEE MTT-S International Microwave and Optoelectronics Conference}, Porto de Galinhas, 2015.}
}
{\bodytext{\bull Y. Fei, A. Fumagalli, M. G. Alabarce, \textbf{B. Sarti}, U. C. Moura, N. G. Gonzalez, and J. R. F. Oliveira, {\href{http://ieeexplore.ieee.org/xpl/login.jsp?tp=&arnumber=7249153&url}{"Estimating EDFA output power with an efficient numerical modeling framework,"}} in \textit{International Conference on Communications}, London, IEEE, pp. 5222-5227, 2015.}
}
{\bodytext{\bull \textbf{B. Sarti}, J. R. F. Oliveira, M. G. Alabarce, Uiara C. Moura, "Processo de calibra\c{c}\~{a}o em campo dos amplificadores Raman distribu\'{i}dos contra-propagantes para opera\c{c}\~{a}o no modo de controle autom\'{a}tico de ganho," INPE Brazil, patent application number BR 10 2015 011437-0, filed on May 2015.
}}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\spacedhrule{1.6em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%       INTERESTS SECTION
%----------------------------------------------------------------------------------------

\roottitle{Other competences and interests} % Top level section

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
%{Non-exhaustive:}
{\textbf{Tennis competitions:}} 
{best {\href{http://www.lequipe.fr/Ilosport/Archives/Actualites/Comprendre-le-classement-francais/742514}{French ranking}}: 15.}

\inlineheadsection
{\textbf{Music:}}
{10 years of musical theory formation at {\href{http://www.amneville-les-thermes.com/le-conservatoire-de-musique-et-de-danse}{Amnéville City music academy}} with validation of the 3 first cycles. Has been playing the trumpet for 7 years and was a member of several orchestras.}

\inlineheadsection
{\textbf{Others:}}
{fitness training, Japanese animations and board games.}

%----------------------------------------------------------------------------------------

\end{document}